### 2015-04-18 implementation-specs.tex

\begin{figure}
\begin{minted}[linenos,
               numbersep=5pt,
			   fontsize=\scriptsize,
               frame=lines,
               framesep=2mm]{python}
class Dyninst(Package):
    """"Dyninst binary instrumentation and analysis tool."""
    url="http://www.paradyn.org/release8.1/DyninstAPI-8.1.1.tgz"
    version('8.1.1', 'd1a04e995b7aa70960cd1d1fac8bd6ac')
    depends_on("libelf")                                                                            
    depends_on("libdwarf")                                                                          
    depends_on("boost@1.42:")

    # default build version uses cmake                                                                        
    def install(self, spec, prefix):
        with working_dir('spack-build', create=True):                                               
            cmake('..', *std_cmake_args)
            make()                                                                                  
            make("install")

    # when version is 8.1 or lower, use configure.                                                                                                    
    @when('@:8.1')                                                                                  
    def install(self, spec, prefix):                                                                
        configure("--prefix=" + prefix)                                                             
        make()                                                                                      
        make("install")     
\end{minted}
\caption{
    Specialized {\tt install} method in Dyninst. 
	\label{fig:specialization}
}
\end{figure}

>>>>

%class Dyninst(Package):
%    """"Dyninst binary instrumentation and analysis tool."""
%    url="http://www.paradyn.org/release8.1/DyninstAPI-8.1.1.tgz"
%    version('8.1.1', 'd1a04e995b7aa70960cd1d1fac8bd6ac')
%    depends_on("libelf")
%    depends_on("libdwarf")
%    depends_on("boost@1.42:")
%
\begin{figure}
\begin{minted}[linenos,
               numbersep=5pt,
			   fontsize=\scriptsize,
               frame=lines,
               framesep=2mm]{python}
    def install(self, spec, prefix):  # default build uses cmake
        with working_dir('spack-build', create=True):
            cmake('..', *std_cmake_args)
            make()
            make("install")

    @when('@:8.1')                    # <= 8.1 uses autotools
    def install(self, spec, prefix):
        configure("--prefix=" + prefix)
        make()
        make("install")
\end{minted}
\caption{
    Specialized {\tt install} method in Dyninst.
	\label{fig:specialization}
}
\end{figure}

### 2015-04-18 implementation-virtual-deps.tex
Concretization section.

\subsection{Versioned Virtual Dependencies}

\begin{figure}
%
\begin{subfigure}{\linewidth}
	\begin{minted}[numbersep=5pt,
	              fontsize=\scriptsize,
	              frame=lines,
                  framesep=2mm]{python}
class Mvapich2(Package):    
    provides('mpi@:2.2', when='@1.9')
    provides('mpi@:3.0', when='@2.0')
\end{minted}
	\caption{%
		{\tt mvapich2} provides {\tt mpi} interface with specific versions.
		\label{fig:virtual-deps-provides}
	}
\end{subfigure}
%
\begin{subfigure}{\linewidth}
	\begin{minted}[numbersep=5pt,
	              fontsize=\scriptsize,
	              frame=lines,
                  framesep=2mm]{python}
class Mpileaks(Package):    
    depends_on('mpi')
\end{minted}
	\caption{%
		{\tt mpileaks} depends on any MPI version.
		\label{fig:virtual-deps-mpileaks}
	}
\end{subfigure}
%
\begin{subfigure}{\linewidth}
	\begin{minted}[numbersep=5pt,
	              fontsize=\scriptsize,
	              frame=lines,
                  framesep=2mm]{python}
class Gerris(Package):
    depends_on('mpi@2:')
\end{minted}
	\caption{%
		Gerris CFD solver requires MPI at version 2 or higher.
		\label{fig:virtual-deps-depends}
	}
\end{subfigure}
%
\caption{
	Virtual dependencies.
	\label{fig:virtual-deps}
}
\end{figure}

@@

Figure~\ref{fig:virtual-deps-provides} shows how packages can provide
virtual interfaces in Spack.  The spec syntax is used to concisely
associate a range of {\tt mpi} versions (up to 2.2) with Mvapich version 1.9.
In Figure~\ref{fig:virtual-deps-mpileaks}, we see that {\tt mpileaks} requires
MPI but is unconstrained on version.  Since this spec satisfies the constraints in 
the {\tt mvapich2} package, {\tt Mvapich2} can be used to satisfy the {\tt mpi}
dependency in {\tt mpileaks}.  Similarly, the Gerris CFD library needs MPI
at version 2 or higher -- either {\tt mvapich2} 1.9 or 2.0 can be used to satisfy
this constrained dependency.

>>>>

\subsection{Versioned Virtual Dependencies}\label{sec:virtual}

\begin{figure}
	\begin{minted}[numbersep=5pt,
	              fontsize=\scriptsize,
	              frame=lines,
                  framesep=2mm]{python}
 # providers of mpi                       # mpi dependents
 class Mvapich2(Package):                 class Mpileaks(Package):
     provides('mpi@:2.2', when='@1.9')        depends_on('mpi')
     provides('mpi@:3.0', when='@2.0')           ...
     ...                                  class Gerris(Package):
 class Mpich(Package):                        depends_on('mpi@2:')
     provides('mpi@:3', when='@3:')           ...
     provides('mpi@:1', when='@1:')
     ...
\end{minted}
\caption{
	Virtual dependencies.
	\label{fig:virtual-deps}
}
\end{figure}

@@

Figure~\ref{fig:virtual-deps} shows how packages provide
virtual interfaces in Spack.  The spec syntax is used to concisely
associate ranges of {\tt mpi} versions {\tt mvapich2} and {\tt mpich}
The {\tt mpileaks} package requires {\tt mpi} but it does not constrain the version.
Any version of {\tt mvapich2} or {\tt mpich} could be used to to satisfy the {\tt mpi}
constraint. The Gerris CFD library, however, needs MPI version 2 or higher.  So any
version except {\tt mpich} 1.x could be used to satisfy the constrained dependency.

%{\bf Dependencies.}
%Lines 6 and 7 in the table show the key feature that enables Spack's flexibility.
%The user can specify all of the above information not only for the package being
%installed, but also for its {\it dependencies}.  To do this, the user needs only supply 
%\verb|^| and the dependency's name.  If we need to build a new version with a specific
%version of {\tt mvapich2}, we can simply add, e.g., \verb|^mvapich2@1.9|
%to the spec, and it will build with that MPI version instead of the default.
%This can also be done for multiple libraries in the same spec (line 7).
